---
title       : Interesting Facts about Iris
subtitle    : My Shiny App - a coursera data product project
author      : wx-chen
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : [bootstrap, quiz, shiny, interactive]  
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets: {rCharts: [libraries/nvd3]}
---

## Overview  
  
  
### The App: Interesting Facts about Iris:  

* Use the "iris" dataset  
* Provide interactive control of plotted data, and whether to display images of iris flowers  
* Here is the first few lines of the "iris" dataset:

```{r}
library(datasets)
head(iris)
```

--- .class #id 

## Reshape data into a clean format  

* The dataset is melted so that each row contains observations for 1 part (Petal or Sepal)  
```{r, echo=FALSE}
require(dplyr) # use the "dplyr" package
datas <- iris %>%
        select(Sepal.Length,Sepal.Width,Species) %>%
        mutate(Length=Sepal.Length, Width=Sepal.Width, Part="Sepal") %>%
        select(Length, Width, Part, Species)
datap <- iris %>%
        select(Petal.Length,Petal.Width,Species) %>%
        mutate(Length=Petal.Length, Width=Petal.Width, Part="Petal") %>%
        select(Length, Width, Part, Species)
irisdata <- rbind(datas,datap)
```
```{r}
head(irisdata,3)
tail(irisdata,3)
```

---

## Use the dropdown menu to control plot
* You can choose if you want to see the dimension plots of one iris species, or all three together  
* e.g. choose to see all three species, plot will be like:  
```{r, echo=FALSE,results='asis'}
require(ggplot2)
g <- ggplot(irisdata,aes(Width, Length))
g + geom_point(aes(color=Species)) + facet_grid(.~Part)
```

---

## Use the Checkbox to display images
* You can choose to display the images of the iris by using the checkbox  
* e.g. if selected this image will be displayed:  

![alt text][1]  

### For more information, go to the app [here](https://chenwx.shinyapps.io/IrisDisplay/)  


[1]: I:/R/IrisSlidify/setose.png "Iris Species"  



